A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-09-30 paper.tex
Rephrase Accel time complexity and issues

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and ECDSA P-256 for digital signature. In this E2EE protocol, ECDSA would take constant time, since the string needed to be signed is in fixed length. HMAC and AES-CBC are the procedures that cost most of the elapsed time. Time complexity of HMAC with SHA-256 is $O(n)$.\cite{hmac_time_complexity} Block cipher takes constant time for a single block which causes the time complexity is $O(n)$, too. Therefore, the E2EE protocol takes only linear time versus arbitrary string length.

\subsubsection{Issues in End-to-End-Encryption}
E2EE helps a lot for low-level edge devices utilizing blockchain service. It dramatically reduces the execution time encryption takes. However, there are some challenges in the E2EE process. Tampering the messages which have conducted E2EE would be a challenging mission. However, spamming would be the critical issue participants may meet under this architecture. It is risky for an edge device connects to an Accel which is operated by an unknown third-party. Sharing Channel Chain ownership with an unknown third-party would allow them to spam on the MAM Channel Chain. Spam would cause subscribers to waste plenty of time on decrypting useless messages. To prevent edge devices from the annoying attack, connecting to a known, trustworthy Accel would be the easiest solution.

>>>>

\subsubsection{Time Complexity}
In this paper, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption, and ECDSA P-256 for digital signature. EDSA would take constant time, since the input is fixed length. The time complexity of HMAC with SHA-256 is $O(n)$\cite{hmac_time_complexity}, and block cipher takes constant time for a single block with time complexity $O(n)$. Therefore, the E2EE protocol takes only linear time versus arbitrary string length.

\subsubsection{Issues in End-to-End-Encryption}
E2EE dramatically reduces the execution time of encryption that lowers the barries of utilizing blockchain service for low-level devices. However, Accel can tamper the messages and even spam on the requester's MAM channel, where its root is given to Accel at start. Significantly, it is risky for an edge device to connect to an Accel operating by an unknown third-party, thus connecting to a known, trustworthy Accel would be the easiest solution to prevent such attacks.
